Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation4.tex
presentation seminar Annemie

\title{Drought and its Effects on Economy}  
\author{Monika Novackova} 
\date{December 2017} 
\institute{University of Sussex}

@@

\begin{frame}\label{My Interest}

\large{My research interest:} \\
\vspace{0.7cm}

\large{\hspace{1cm}\textbf{Effects of droughts on economy in Kenya}}
\end{frame}
\note{A}

@@

\section{Definition of Drought}

\begin{frame}\label{Definition of Drought}
\frametitle{Definition of Drought} 
 \begin{itemize}
\item Hi
\end{itemize}

@@

\note{a\\
b}

@@

\frametitle{My suggestion - panel estimation}\label{MySuggestion3}

\begin{itemize}
\item Dummy variable (0/1) drought occurred in a particular county and year or not

\item \textbf{Units of analysis:} Counties in Kenya $\times$ year

\item \textbf{Control variables ? - subject to availability}

\begin{itemize}
\item GDP, soil quality data, population,average land area, average value assets,  climate, degree days?
\end{itemize}

\item \textbf{Estimation methods}

\begin{itemize}
\item Fixed effects, SURE, Kalman filter, Box-Jenkins
\end{itemize}

>>>>

\title{Effects of Weather on Maize Yield in Kenya}  
\author{Monika Novackova \\ \footnotesize supervised by: \textcolor{darkblue}{Pedram Rowhani, Martin Todd and Annemie Maertens}}

\date{January 2019} 
\institute{University of Sussex}

@@

@@

\section{Introduction}

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

\begin{frame}\label{Introduction}
\frametitle{Introduction} 
 \begin{itemize}
\item SSRP project, related to ForPAc project
\item Extreme weather $\rightarrow$ disasters \textcolor{red}{(maybe name some years of drought in Kenya??)}

\begin{itemize}
\item Early warning systems have been developed
\end{itemize}
\item Goals: Improve early warning systems in Kenya
\item Shifting the disaster management from reactive to protective
\end{itemize}

\begin{itemize}
\item Various approaches considered including:

\begin{itemize}
\item Relating NDMA Early warning phase classification to weather
\item Relating markets and food prices to weather
\item Relating maize yields to weather to weather
\item Computable general equilibrium (CGE) models
\end{itemize}
\end{itemize}
\end{frame}

\note{Climate change has been increasing amplitudes and frequency of extreme weather events\\ Not every hazard turns into disaster\\
Relating NDMA Early warning classification to weather also various precip and weather indexes
r
b}

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

\begin{frame}
       \hspace{-0.8cm}  \textbf{NDMA Early Warning Phase\\ \hspace{-0.8cm} Classification}

\vspace{-0.9cm}
     \begin{figure}
      \begin{columns}
        \column{.4\linewidth}

  \caption*{\textcolor{DarkGreen}{\textbf{\underline{\small{Example: Kitui county}}}}\\

 \vspace{0.25cm}\hspace{-0.25cm} \textbf{\textit{\textcolor{blue}{Normal $\rightarrow$ Alert $\rightarrow$  Alarm}}} \\
   \vspace{0.4cm}  
 \hspace{-0.25cm}  $\bullet$ \small{Bulletins for ASAL counties} \\
   \hspace{-0.25cm}  $\bullet$ \small{Online since 2013} \\
     \vspace{0.1cm}  
  \hspace{0.15cm}    \footnotesize{$\bullet$ But in pdf format} \\ 
    \vspace{0.1cm}  
\hspace{-0.25cm}   \small{$\bullet$ For county and month}

 }
        \column{.6\linewidth}

    \vspace{-0.16cm}   \hspace{-0.1cm}   \includegraphics[width = 0.9\textwidth]{PhaseNA.png}  %565*238
 \vspace{-0.3cm}  
      \end{columns}
    \end{figure}

\vspace{-1.3cm}
    \begin{figure}
      \begin{columns}
        \column{.5\linewidth }

  \vspace{-1.8cm}        
        \column{.5\linewidth}

  \hspace{-2.6cm}  \includegraphics[width = 1.2\textwidth]{PrecNA.png}  %565*238
      \end{columns}
    \end{figure}

@@

\note{This is an example of one of the approaches that we eventually abandoned\\
b}

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

\begin{frame}\label{Approach}
\frametitle{Approach}

\begin{itemize}
\item Narrowing the research question:
\begin{itemize}
\item Relationship of maize yield and weather in Kenya

\begin{itemize}
\item What is it about weather that causes drought related disasters?
\item Which particular characteristics of weather are the most 'responsible' for drought related disasters?
\end{itemize}
\end{itemize}
\end{itemize}

Sample:
\begin{itemize}
\item Panel of 47 counties of Kenya, $1981-2017$
\end{itemize}

\note{After various problems with data (prices - not for every county, NDMA phases - not much of an objective criterion, probably political, various VCI values)
\\ so the decision about the approach was partially driven by data (un)availability}

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

@@
